---
title: "WFA Statistics"
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
runtime: shiny
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = 'center')
if (!require("pacman")) install.packages("pacman")
pacman::p_load(flexdashboard, tidyverse)
```



<!-- vertical_layout: fill -->
<!-- logo: www/tractor_resized.png -->
<!-- favicon: www/tractor_resized.png -->
<!-- social: menu -->
<!-- css: styles.css -->


About {data-navmenu="Home"}
=====================================

League Overview {data-navmenu="Home"}
=====================================

Top Performers {data-navmenu="Home"}
=====================================


<!-- OFFENSE -->

League {data-navmenu="Offense"}
=====================================

By Division {data-navmenu="Offense"}
=====================================

By Team {data-navmenu="Offense"}
=====================================

By Position {data-navmenu="Offense"}
=====================================

By Player {data-navmenu="Offense"}
=====================================


<!--  DEFENSE -->

League {data-navmenu="Defense"}
=====================================

By Division {data-navmenu="Defense"}
=====================================

By Team {data-navmenu="Defense"}
=====================================

By Position {data-navmenu="Defense"}
=====================================

By Player {data-navmenu="Defense"}
=====================================

Column {.tabset}
-------------------------------------

### Season 

```{r}
print("offensive stats")
```


### Comparison

```{r}
plot(mtcars$mpg, mtcars$wt)
```




League {data-navmenu="Special Teams"}
=====================================

By Division {data-navmenu="Special Teams"}
=====================================

By Team {data-navmenu="Special Teams"}
=====================================

Column {.tabset}
-------------------------------------

### Kick-off/return

```{r}
print("offensive stats")
```


### Punt

```{r}
plot(mtcars$mpg, mtcars$wt)
```

### Kicking

```{r}
plot(mtcars$mpg, mtcars$wt)
```




Prediction {data-navmenu="Analytics"}
=====================================

Team Rankings {data-navmenu="Analytics"}
=====================================

Player Rankings {data-navmenu="Analytics"}
=====================================



