---
title: "WFA Statistics"
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
runtime: shiny
---


```{r setup, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
library(flexdashboard)
library(knitr)
library(shiny)
library(tidyverse)
library(DT)
library(rsconnect)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = 'center', fig.dim = c(4, 6) )


# set the theme for all ggplots: 
theme_set(theme_minimal() +
            theme(plot.title = element_text(hjust = 0.5)
                  , axis.text = element_text(size = 10)
                  , axis.title=element_text(size=14,face="bold")))

source("data_prep.R")
#pass.sum.dta <- read_csv("PassingDataTemp.csv")
#rsconnect::setAccountInfo(name='connorjo',
#			  token='966F109BEA1433280CB80AACEF59B28F',
#			  secret='7l/D0vouhjiFkeEZwmyB0anPqXFAXJogfqqifjN7')
#rsconnect::deployApp('wfa_dash.Rmd')
```



<!-- Sidebar {.sidebar} -->
<!-- ===================================== -->


<!-- logo: www/tractor_resized.png -->
<!-- favicon: www/tractor_resized.png -->
<!-- social: menu -->
<!-- css: styles.css -->


About {data-navmenu="Home"}
=====================================

We are currently only looking at the 2018 season (end of season). 

_Pages that contain some content_

* Offense:
    +  Quarterbacks
    +  Runningbacks
    +  Widereceivers
    
League Overview {data-navmenu="Home"}
=====================================

Top Performers {data-navmenu="Home"}
=====================================


<!-- OFFENSE -->

Overall {data-navmenu="Offense"}
=====================================


Inputs {.sidebar data-width=250}
----------------------------------------------------------------------


Quarterbacks {data-navmenu="Offense" data-orientation=rows}
=====================================


Inputs {.sidebar data-width=250}
-----------------------------------------------------------------------


```{r passing.input}
# What players (QBs) will be compared/analyzed
selectInput("player", "QB (>50 attempts)", choices = c('', unique(pass.sum.dta$Player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("comp", "Compare to another QB", value = FALSE)

# Player rankings on side: 


conditionalPanel(
      condition = "input.comp",
      selectInput("comp.plyr", ""
            , choices =  c('', unique(pass.sum.dta$Player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))



# All weeks for the players selected
temp.dta <- reactive({
    dta <- pass.sum.dta %>% 
                filter(Player %in% c(input$player, input$comp.plyr)) %>%
                ungroup
    
    dta
  })

# Only the last week played of data for the players selected
temp.last.dta <- reactive({
  temp.dta() %>%
      group_by(Player) %>%
      top_n(1, as.numeric(game)) %>%
      ungroup
})

# A table of the rating of the QB, by passer rating (last weeks data)
temp.comp.dta <- reactive({
  temp.df <- temp.last.dta() %>%
                select(plyr.lbl, Games = game, Rating = qb.rate.cum
                       , Attempts = Att.cum
                       , `Comp (%)` = comp.cum.rate, TD = TD.cum
                       , `Avg Yds` = avg.cum) %>% 
      t
            
      plyr.names <- temp.df[1, ]
      
      temp.df <- temp.df %>%
        data.frame()
      
      names(temp.df) <- plyr.names
      
      temp.df %>%
        rownames_to_column("Stat") %>%
        filter(Stat != "plyr.lbl") 
})

renderTable(
  if(input$player != '' | input$comp.plyr != '') {temp.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}
```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.last.dta() %>% 
             filter(Player == input$player) %>%
             select(team)
  valueBox(value
           , icon = "fa-football-ball")
})

```

### Total Passing Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.last.dta() %>% 
             filter(Player == input$player) %>%
             select(Yds.cum)
  valueBox(value
           , icon = "fa-football-ball")
})

```


### Total Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(temp.last.dta() %>% 
             filter(Player == input$player) %>%
             select(TD.cum)
           , icon = "fa-football-ball")
})
```

### Player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```


Row {data-height=250}
-----------------------------------------------------------------------

### Total passing yards vs. passing attempts


```{r passyrds.plot}
renderPlot({

  temp.last.dta() %>%
    ggplot(aes(x = Att.cum, y = Yds.cum
               , label = plyr.lbl, color = Player)) +
    
    # plots all of the players in grey with a red line for the lm
    geom_point(data = pass.sum.dta %>%
                group_by(Player) %>%
                filter(Player != input$player) %>%
                top_n(1, week)
                , mapping = aes(x = Att.cum, y = Yds.cum)
                , color = "grey") +
    geom_smooth(data = pass.sum.dta %>%
                group_by(Player) %>%
                top_n(1, week)
                , mapping = aes(x = Att.cum, y = Yds.cum)
                , method = "lm", se = FALSE, color = "red") +
    
    # plot the selected players
    geom_point(size = 3) +
    geom_text(nudge_y = 100) +
    labs(x = "Total Attempts", y = "Total Yards"
         , caption = "Grey dots represent all non-selected QBs") +
    coord_cartesian(xlim = c(50, pass.att.max)
                    , ylim = c(pass.yrd.min, pass.yrd.max)) +
    scale_color_discrete(guide = FALSE) 
})
```


### Touchdown Rate/Interception Rate

```{r td.int.plot}
renderPlot({
  var.by.game.plot(temp.dta(), pass.sum.dta
                 , TD.Int.cum, "Ratio", c(0,15))
})
```

Row {data-height=250}
--------------------------------------------------------

### QB Rating Cumulative
 
```{r}
renderPlot({
  var.by.game.plot(temp.dta(), pass.sum.dta
                 , qb.rate.cum, "QB Rating", c(0,168))
})
```
  

Running Backs {data-navmenu="Offense" data-orientation=rows}
=====================================


Inputs {.sidebar data-width=250}
-----------------------------------------------------------------------


```{r rushing.input}
# What players (QBs) will be compared/analyzed
selectInput("rb", "RB (>50 Carries)", choices = c('', unique(rush.sum.dta$Player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("comprb", "Compare to another RB", value = FALSE)

# Player rankings on side: 


conditionalPanel(
      condition = "input.comprb",
      selectInput("comp.rb", ""
            , choices =  c('', unique(rush.sum.dta$Player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))



# All weeks for the players selected
temp.rb.dta <- reactive({
    dta <- rush.sum.dta %>% 
                filter(Player %in% c(input$rb, input$comp.rb)) %>%
      ungroup
    
    dta
  })

# Only the last week played of data for the players selected
temp.rb.last.dta <- reactive({
  temp.rb.dta() %>%
      group_by(Player) %>%
      top_n(1, as.numeric(game)) %>%
      ungroup
})

# A table of the rating of the QB, by passer rating (last weeks data)
temp.rb.comp.dta <- reactive({
  temp.df <- temp.rb.last.dta() %>%
                select(plyr.lbl, Games = game, Carries = car.cum
                  , TD = TD.cum, `Avg Yds` = avg.cum, `Yds per Game` = yds.cum.game) %>% 
      t
            
      plyr.names <- temp.df[1, ]
      
      temp.df <- temp.df %>%
        data.frame()
      
      names(temp.df) <- plyr.names
      
      temp.df %>%
        rownames_to_column("Stat") %>%
        filter(Stat != "plyr.lbl") 
})

renderTable(
  if(input$rb != '' | input$comp.rb != '') {temp.rb.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}
```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.rb.last.dta() %>% 
             filter(Player == input$rb) %>%
             select(team)
  valueBox(value
           , icon = "fa-football-ball")
})

```

### Total Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.rb.last.dta() %>% 
             filter(Player == input$rb) %>%
             select(yds.cum)
  valueBox(value
           , icon = "fa-football-ball")
})

```


### Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(temp.rb.last.dta() %>% 
             filter(Player == input$rb) %>%
             select(TD.cum)
           , icon = "fa-football-ball")
})
```

### Player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```


Row {data-height=350}
-------------------------------------------------------------


### Rushing Yards by Game

```{r rush.yrds.game}
renderPlot({
  var.by.game.plot(temp.rb.dta(), rush.sum.dta
                 , as.numeric(Yards), "Yards", c(0,300))
})
```

### Rushing Yards per Carry by Game
```{r rush.yrds.car}
renderPlot({
  var.by.game.plot(temp.rb.dta(), rush.sum.dta
                 , yds.car, "Yards", c(0,30))
})
```


Wide Receivers {data-navmenu="Offense" data-orientation=rows}
=====================================




Inputs {.sidebar data-width=250}
-----------------------------------------------------------------------


```{r receiving.input}
# What players (QBs) will be compared/analyzed
 selectInput("wr", "WR (>10 Receptions)", choices = c('', unique(rec.sum.dta$Player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("compwr", "Compare to another Receiver", value = FALSE)

# Player rankings on side: 


conditionalPanel(
      condition = "input.compwr",
      selectInput("comp.wr", ""
            , choices =  c('', unique(rec.sum.dta$Player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))



# All weeks for the players selected
temp.wr.dta <- reactive({
    dta <- rec.sum.dta %>% 
                filter(Player %in% c(input$wr, input$comp.wr)) %>%
      ungroup
    dta
  })

# Only the last week played of data for the players selected
temp.wr.last.dta <- reactive({
  temp.wr.dta() %>%
      group_by(Player) %>%
      top_n(1, as.numeric(game)) %>%
      ungroup
})

# A table of the rating of the QB, by passer rating (last weeks data)
temp.wr.comp.dta <- reactive({
  temp.df <- temp.wr.last.dta() %>%
                select(plyr.lbl, Games = game, Receptions = rec.cum
                  , TD = TD.cum, `Avg Yds` = avg.cum, `Yds per Game` = yds.cum.game) %>% 
      t
            
      plyr.names <- temp.df[1, ]
      
      temp.df <- temp.df %>%
        data.frame()
      
      names(temp.df) <- plyr.names
      
      temp.df %>%
        rownames_to_column("Stat") %>%
        filter(Stat != "plyr.lbl") 
})

renderTable(
  if(input$wr != '' | input$comp.wr != '') {temp.wr.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.wr.last.dta() %>% 
             filter(Player == input$wr) %>%
             select(team)
  valueBox(value
           , icon = "fa-football-ball")
})

```

### Total Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.wr.last.dta() %>% 
             filter(Player == input$wr) %>%
             select(yds.cum)
  valueBox(value
           , icon = "fa-football-ball")
})

```


### Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(temp.wr.last.dta() %>% 
             filter(Player == input$wr) %>%
             select(TD.cum)
           , icon = "fa-football-ball")
})
```

### Player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```

Row {data-height=350}
-----------------------------------------------------------------


### Yards per game (by single game)

```{r}
renderPlot({
  var.by.game.plot(temp.wr.dta(), rec.sum.dta
                 , as.numeric(Yards), "Yards", c(0,200))
})
```

### Yards per Reception (by single game)

```{r}
renderPlot({
  var.by.game.plot(temp.wr.dta(), rec.sum.dta
                 , yds.rec, "Yards", c(0,50))
})
```



Complete Stats {data-navmenu="Offense" data-orientation=rows}
=====================================

Row {.tabset data-height=600}
----------------------------------------------------------------------

### Passing 

```{r}
datatable(pass.sum.dta %>% 
  group_by(Player) %>%
          top_n(1, as.numeric(game)) %>%
          select(Player, Games = game, Rating = qb.rate.cum, Attempts = Att.cum
                 , Comp = comp.cum, Yds = Yds.cum, Avg = avg.cum
                 , TD = TD.cum) %>%
          arrange(desc(as.numeric(Rating)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
          
```


### Rushing

```{r}
datatable(rush.sum.dta %>% 
  group_by(Player) %>%
          top_n(1, as.numeric(game)) %>%
          select(Player, Games = game, Carries = car.cum
                 , Yds = yds.cum, Avg = avg.cum
                 , TD = TD.cum, `Yds per Game` = yds.cum.game) %>%
          arrange(desc(as.numeric(Yds)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
```


### Receiving


```{r}
datatable(rec.sum.dta %>% 
  group_by(Player) %>%
          top_n(1, as.numeric(game)) %>%
          select(Player, Games = game, Recs = rec.cum
                 , Yds = yds.cum, Avg = avg.cum
                 , TD = TD.cum, `Yds per Game` = yds.cum.game) %>%
          arrange(desc(as.numeric(Yds)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
```



<!--  DEFENSE -->

League {data-navmenu="Defense"}
=====================================

By Division {data-navmenu="Defense"}
=====================================

By Team {data-navmenu="Defense"}
=====================================

By Position {data-navmenu="Defense"}
=====================================

By Player {data-navmenu="Defense"}
=====================================


League {data-navmenu="Special Teams"}
=====================================

By Division {data-navmenu="Special Teams"}
=====================================

By Team {data-navmenu="Special Teams"}
=====================================


Prediction {data-navmenu="Analytics"}
=====================================

Team Rankings {data-navmenu="Analytics"}
=====================================

Player Rankings {data-navmenu="Analytics"}
=====================================

