---
title: "WFA Statistics"
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
runtime: shiny
---


```{r setup, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
library(flexdashboard)
library(knitr)
library(shiny)
library(tidyverse)
library(DT)
library(rsconnect)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE
                      , message = FALSE, fig.align = 'center'
                      , fig.dim = c(4, 6))



source("data_prep.R")
#load("tempworkspace.RData")
#rsconnect::setAccountInfo(name='connorjo',
#			  token='966F109BEA1433280CB80AACEF59B28F',
#			  secret='7l/D0vouhjiFkeEZwmyB0anPqXFAXJogfqqifjN7')
#rsconnect::deployApp('wfa_dash.Rmd')
# for working offline: 
# qb.dash.dta <- read_csv("qb.csv")
# rb.dash.dta <- read_csv("rb.csv")
# wr.dash.dta <- read_csv("wr.csv")
# pass.yrd.max <- max(qb.dash.dta$yards_cum)
# pass.yrd.min <- min(qb.dash.dta$yards_cum)
# pass.td.max <- max(qb.dash.dta$td_cum)
# pass.att.max <- max(qb.dash.dta$att_cum)
# source("functions.R")
```



<!-- Sidebar {.sidebar} -->
<!-- ===================================== -->


<!-- logo: www/tractor_resized.png -->
<!-- favicon: www/tractor_resized.png -->
<!-- social: menu -->
<!-- css: styles.css -->


Home {data-orientation=rows}
=====================================

We are currently only looking at the 2018 season (end of season). 

_Pages that contain some content_

* Offense:
    +  Quarterbacks
    +  Runningbacks
    +  Widereceivers
    
All season-to-date individual statistics can be found [here](#stats).


__This tool and all analytics completed are at the mercy of reporting. Not all teams report every game and not all stats for players are reported (e.g. a runningback has one carry, but 150 yards). Also, the accuracy of statistics reported are at the teams' discretion, particularly for defensive statistics. Ideally, a player ranking system at each position would be created; however, on the defensive side of the ball, determining a player's position is nearly impossible.__

_As always the intangibles of a player cannot be measure, neither can their heart_



<!-- OFFENSE -->

Team
=====================================

Inputs {.sidebar data-width=250}
----------------------------------------------------------------------


Quarterbacks {data-navmenu="Individual" data-orientation=rows}
=====================================


Inputs {.sidebar data-width=300}
-----------------------------------------------------------------------


```{r passing.input}
# What players (QBs) will be compared/analyzed
selectInput("qb", "QB (>50 attempts)", choices = c('', unique(qb.dash.dta$player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("comp", "Compare to another QB", value = FALSE)

# player rankings on side: 


conditionalPanel(
      condition = "input.comp",
      selectInput("comp.qb", ""
            , choices =  c('', unique(qb.dash.dta$player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))



# All weeks for the players selected
qb.dta <- reactive({
        qb.dash.dta %>% 
            filter(player %in% c(input$qb, input$comp.qb))
  })


# A table of the rating of the QB, by passer rating (last weeks data)
qb.comp.dta <- reactive({
      qb.dta() %>%   
          group_by(plyr.lbl) %>%
          mutate(yards_cum.rush = max(yards_cum.rush, na.rm = TRUE)) %>%
          select(plyr.lbl, Team = team, Games = game
                 , Rating = qb_rate_cum
                 , Attempts = att_cum
                 , `Pass Yds` = yards_cum
                 , `Pass Yds/G` = yds_cum_game
                 , `Comp (%)` = comp_cum_rate, TD = td_cum
                 ,  Int = int_cum
                 , `Avg` = avg_cum
                 , `Rush Yds` = yards_cum.rush) %>% 
          create.stats.tbl
})

renderTable(
  if(input$qb != '' | input$comp.qb != '') {qb.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}
```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(qb.dta(), input$qb, team)
           , icon = "fa-football-ball")
})

```

### Passing Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(qb.dta(), input$qb, yards_cum)
           , icon = "fa-football-ball")
})

```


### Passing TDs {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(qb.dta(), input$qb, td_cum)
           , icon = "fa-football-ball")
})
```

### Player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```


Row {data-height=250}
-----------------------------------------------------------------------

### Total passing yards vs. passing attempts

```{r}
renderPlot({
  plot.std(qb.dta(), qb.dash.dta
           , att_cum, yards_cum
           , "Attempts", "Yards")
})
```

### Touchdown Rate/Interception Rate

```{r td.int.plot}
renderPlot({
  plot.var.by.game(qb.dta(), qb.dash.dta
                 , td_int_cum, "Ratio")
})
```

Row {data-height=250}
--------------------------------------------------------

### QB Rating (Cumulative)
 
```{r}
renderPlot({
  plot.var.by.game(qb.dta(), qb.dash.dta
                 , qb_rate_cum, "QB Rating")
})
```


### Rushing Yards by game

```{r}
renderPlot({
  plot.var.by.game(qb.dta(), qb.dash.dta
                 , yards_cum.rush, "Yards")
})
```





Running Backs {data-navmenu="Individual" data-orientation=rows}
=====================================


Inputs {.sidebar data-width=300}
-----------------------------------------------------------------------


```{r rushing.input}
# What players (QBs) will be compared/analyzed
selectInput("rb", "RB (>25 Carries)", choices = c('', unique(rb.dash.dta$player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("comprb", "Compare to another RB", value = FALSE)

# player rankings on side: 


conditionalPanel(
      condition = "input.comprb",
      selectInput("comp.rb", ""
            , choices =  c('', unique(rb.dash.dta$player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))

# All weeks for the players selected
rb.dta <- reactive({
   rb.dash.dta %>% 
        filter(player %in% c(input$rb, input$comp.rb))
  })

# A table of the rating of the QB, by passer rating (last weeks data)
rb.comp.dta <- reactive({
  rb.dta() %>%
      select(plyr.lbl, Team = team, Games = game
             , Carries = carries_cum, TD = td_cum
             , Avg = avg_cum, `Yds/G` = yds_cum_game) %>% 
      create.stats.tbl
})

renderTable(
  if(input$rb != '' | input$comp.rb != '') {rb.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}
```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(rb.dta(), input$rb, team)
           , icon = "fa-football-ball")
})

```

### Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(rb.dta(), input$rb, yards_cum)
           , icon = "fa-football-ball")
})

```


### Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(rb.dta(), input$rb, td_cum)
           , icon = "fa-football-ball")
})
```

### player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```


Row {data-height=250}
-------------------------------------------------------------


### Rushing Yards by Game

```{r rush.yrds.game}
renderPlot({
  plot.var.by.game(rb.dta(), rb.dash.dta
                 , yards, "Yards")
})
```

### Rushing Yards per Carry by Game
```{r rush.yrds.car}
renderPlot({
  plot.var.by.game(rb.dta(), rb.dash.dta
                 , yds_car, "Yards")
})
```

Row {data-height=250}
--------------------------------------------------------

### TD by Carries (season)
 
```{r}
renderPlot({
  plot.std(rb.dta(), rb.dash.dta
           , carries_cum, td_cum
           , "Carries", "TD")
})
```


### Attempts by Game

```{r}
renderPlot({
  plot.var.by.game(rb.dta(), rb.dash.dta
                 , carries, "Carries")
})
```





Wide Receivers {data-navmenu="Individual" data-orientation=rows}
=====================================

Inputs {.sidebar data-width=300}
-----------------------------------------------------------------------

```{r wr.input}
# What players (QBs) will be compared/analyzed
 selectInput("wr", "WR (>10 Receptions)", choices = c('', unique(wr.dash.dta$player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

checkboxInput("compwr", "Compare to another Receiver", value = FALSE)

# player rankings on side: 


conditionalPanel(
      condition = "input.compwr",
      selectInput("comp.wr", ""
            , choices =  c('', unique(wr.dash.dta$player))
            , selected = NULL, multiple = FALSE
            , selectize = TRUE))



# All weeks for the players selected
wr.dta <- reactive({
    dta <- wr.dash.dta %>% 
                filter(player %in% c(input$wr, input$comp.wr)) %>%
      ungroup
    dta
  })


# A table of the rating of the QB, by passer rating (last weeks data)
wr.comp.dta <- reactive({
  wr.dta() %>%
      select(plyr.lbl, Team = team, Games = game
             , Receptions = rec_cum, TD = td_cum
             , `Avg Yds` = avg_cum
             , `Yds/G` = yds_cum_game) %>% 
      create.stats.tbl
})

renderTable(
  if(input$wr != '' | input$comp.wr != '') {wr.comp.dta()}
)


```


Row {data-height=100}
-----------------------------------------------------------------------

### Team {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(wr.dta(), input$wr, team)
           , icon = "fa-football-ball")
})

```

### Total Yards {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({ 
  valueBox(get.value(wr.dta(), input$wr, yards_cum)
           , icon = "fa-football-ball")
})

```


### Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(get.value(wr.dta(), input$wr, td_cum)
           , icon = "fa-football-ball")
})
```

### player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-trophy")
})
```

Row {data-height=250}
-----------------------------------------------------------------


### Yards per game (by single game)

```{r}
renderPlot({
  plot.var.by.game(wr.dta(), wr.dash.dta
                 , yards, "Yards")
})
```

### Yards per Reception (by single game)

```{r}
renderPlot({
  plot.var.by.game(wr.dta(), wr.dash.dta
                 , yds_rec, "Yards")
})
```



Row {data-height=250}
--------------------------------------------------------

### TD by Carries (season)
 
```{r}
renderPlot({
  plot.std(wr.dta(), wr.dash.dta
           , td_cum, rec_cum
           , "TD", "Receptions")
})
```


### Attempts by Game

```{r}
renderPlot({
  plot.var.by.game(wr.dta(), wr.dash.dta
                 , rec, "Receptions")
})
```



Defensive Players {data-navmenu="Individual" data-orientation=rows}
=====================================

Specialists {data-navmenu="Individual"}
=====================================


Prediction {data-navmenu="Analytics"}
=====================================

Team Rankings {data-navmenu="Analytics"}
=====================================

Player Rankings {data-navmenu="Analytics"}
=====================================

<!-- this page is being linked to:  -->
Stats {.hidden data-orientation=rows}
=====================================

Row {.tabset data-height=600}
----------------------------------------------------------------------

### Passing 

```{r}
datatable(qb.dash.dta %>% 
  group_by(player) %>%
          top_n(1, as.numeric(game)) %>%
          select(player, Team = team, Games = game
                 , Rating = qb_rate_cum, Attempts = att_cum
                 , Comp = comp_cum, Yds = yards_cum, Avg = avg_cum
                 , TD = td_cum) %>%
          arrange(desc(as.numeric(Rating)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
          
```


### Rushing

```{r}
datatable(rb.dash.dta %>% 
  group_by(player) %>%
          top_n(1, as.numeric(game)) %>%
          select(player, Team = team, Games = game, Carries = carries_cum
                 , Yds = yards_cum, Avg = avg_cum
                 , TD = td_cum, `Yds per Game` = yds_cum_game) %>%
          arrange(desc(as.numeric(Yds)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
```


### Receiving


```{r}
datatable(wr.dash.dta %>% 
  group_by(player) %>%
          top_n(1, as.numeric(game)) %>%
          select(player, Team = team, Games = game, Recs = rec_cum
                 , Yds = yards_cum, Avg = avg_cum
                 , TD = td_cum, `Yds per Game` = yds_cum_game) %>%
          arrange(desc(as.numeric(Yds)))
  , options = list(bPaginate = FALSE, pageLength = 10), fillContainer = TRUE)
```




