---
title: "WFA Statistics"
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    vertical_layout: scroll
    orientation: rows
runtime: shiny
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = 'center')
if (!require("pacman")) install.packages("pacman")
pacman::p_load(flexdashboard, tidyverse)

source("01_Data_Prep.R")
#pass.sum.dta <- read_csv("PassingDataTemp.csv")

```



<!-- Sidebar {.sidebar} -->
<!-- ===================================== -->


<!-- vertical_layout: fill -->
<!-- logo: www/tractor_resized.png -->
<!-- favicon: www/tractor_resized.png -->
<!-- social: menu -->
<!-- css: styles.css -->


About {data-navmenu="Home"}
=====================================

We are currently only looking at the 2018 season. 

League Overview {data-navmenu="Home"}
=====================================

Top Performers {data-navmenu="Home"}
=====================================


<!-- OFFENSE -->

Overall {data-navmenu="Offense"}
=====================================

Passing {data-navmenu="Offense"}
=====================================


Inputs {.sidebar data-width=300}
-----------------------------------------------------------------------

QB Comparisons

```{r passing.input}
# What players (QBs) will be compared/analyzed
selectInput("player", "Player", choices = c('', unique(pass.sum.dta$Player))
              , selected = NULL, multiple = FALSE, selectize = TRUE)

# Player rankings on side: 
selectInput("comp.plyr", "Comparison Player(s)"
            , choices =  unique(pass.sum.dta$Player)
            , selected = NULL, multiple = TRUE
            , selectize = TRUE)



# All weeks for the players selected
temp.dta <- reactive({
    dta <- pass.sum.dta %>% 
                filter((Player == input$player)
                                        | (Player %in% input$comp.plyr)) %>%
                mutate(plyr.of.interest = 
                         case_when(
                            Player == input$player ~ input$player
                            , TRUE                 ~ "Other")
                ) %>%
      ungroup
    
    dta
  })

# Only the last week played of data for the players selected
temp.last.dta <- reactive({
  temp.dta() %>%
      group_by(Player) %>%
      top_n(1, week) %>%
      ungroup
})

# A table of the rating of the QB, by passer rating (last weeks data)
renderTable(temp.last.dta() %>%
              group_by(Player) %>%
              select(`QB Rating` = Rating) %>%
              arrange(desc(as.numeric(`QB Rating`))))

```


Row
-----------------------------------------------------------------------

### Total Passing Yards {.value-box}

<!-- data-width=200 -->

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  value <- temp.last.dta() %>% 
             filter(Player == input$player) %>%
             select(Yds.cum)
  valueBox(value
           , icon = "fa-tag")
})

```


### Total Touchdowns {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox(temp.last.dta() %>% 
             filter(Player == input$player) %>%
             select(TD.cum)
           , icon = "fa-tag")
})
```

### Player Ranking {.value-box}

```{r}
# A box showing the total cumulative yards for the selected player
renderValueBox({
  valueBox("TBD"
           , icon = "fa-tag")
})
```


Row
-----------------------------------------------------------------------

```{r}
renderPlot({

   temp.last.dta() %>%
    ggplot(aes(x = Att.cum, y = Yds.cum
              
               , label = Player)) +
    geom_point(size = 3 , aes(color = factor(plyr.of.interest))) +
    geom_text(nudge_x = 5) +
    labs(x = "Total Attempts", y = "Total Yards"
         , title = "Total Yards vs. Attempts\n (Season-To-Date") +
    coord_cartesian(xlim = c(0, pass.att.max)
                    , ylim = c(0, pass.yrd.max)) +
    scale_color_discrete(guide = FALSE) +
     geom_smooth(data = pass.sum.dta %>%
                group_by(Player) %>%
                top_n(1, week)
                , mapping = aes(x = Att.cum, y = Yds.cum)
                , method = "lm", se = FALSE, color = "red")
})
```



```{r td.int.plot}
renderPlot({

   temp.dta() %>%
    ggplot(aes(x = game, y = TD.Int.cum
               , label = Player)) +
    geom_point(size = 3 
               , aes(color = factor(Player))) +
    geom_line(aes(color = factor(Player))) +
    # geom_text(nudge_x = 5) +
    labs(x = "Game Number"
         , y = "TD Rate/Interception Rate Ratio"
         , title = "Ratio of TD & Interceptions\n Per Attempt") +
    coord_cartesian(xlim = c(0, 8)
                    , ylim = c(0, 15)) +
    scale_color_discrete(guide = FALSE) +
     geom_smooth(data = pass.sum.dta 
                , mapping = aes(x = game, y = TD.Int.cum)
                , method = "loess", se = FALSE, color = "red")
})
```


Rushing {data-navmenu="Offense"}
=====================================

Receiving {data-navmenu="Offense"}
=====================================


<!--  DEFENSE -->

League {data-navmenu="Defense"}
=====================================

By Division {data-navmenu="Defense"}
=====================================

By Team {data-navmenu="Defense"}
=====================================

By Position {data-navmenu="Defense"}
=====================================

By Player {data-navmenu="Defense"}
=====================================

Column {.tabset}
-------------------------------------

### Season 

```{r}
print("offensive stats")
```


### Comparison

```{r}
plot(mtcars$mpg, mtcars$wt)
```




League {data-navmenu="Special Teams"}
=====================================

By Division {data-navmenu="Special Teams"}
=====================================

By Team {data-navmenu="Special Teams"}
=====================================

Column {.tabset}
-------------------------------------

### Kick-off/return

```{r}
print("offensive stats")
```


### Punt

```{r}
plot(mtcars$mpg, mtcars$wt)
```

### Kicking

```{r}
plot(mtcars$mpg, mtcars$wt)
```




Prediction {data-navmenu="Analytics"}
=====================================

Team Rankings {data-navmenu="Analytics"}
=====================================

Player Rankings {data-navmenu="Analytics"}
=====================================

